Bird beak's elaboration and innovation

### 2022-04-27 Analysis/05-Figure2_with_lambdas.Rmd
Update 05-Figure2_with_lambdas.Rmd

```{r, echo = FALSE, eval = TRUE, fig.height = 12, fig.width = 6}
## Summarising the lambdas
load(file = "../Data/Processed/lambda_distributions.rda")

>>>>

```{r, echo = FALSE, eval = TRUE, fig.height = 18, fig.width = 12}
## Summarising the lambdas
load(file = "../Data/Processed/lambda_distributions.rda")
